Neuroevolution in a simple two-player game situation

### 2019-01-07 documentation/paper.tex

\maketitle
\todo{think about good title}

@@

The game comes bundled with a number of bots with different styles, that are designed to pose a challenge to a wide range of human opponents. In order to define a clean ranking between them, we recorded the score of all possible lineups (figure \ref{tab:bot_vs_bot}).
\todo{explain the table}

\begin{figure}[H]
\begin{tabular}{c|ccccccc}
vs. &
\texttt{Axji-0-2} &
\texttt{COM\_11} &
\texttt{GintonicV9} &
\texttt{Hypo14} &
\texttt{reduced} &
\texttt{Union} &
\texttt{trainer} \\
\hline
\texttt{Axji-0-2} & - & 0 & 0 & 4 & 0 & 0 & 10 \\
\texttt{COM\_11} & 21 & - & 9 & 19 & 6 & 16 & 20 \\
\texttt{GintonicV9} & 21 & 12 & - & 19 & 6 & 16 & 20 \\
\texttt{Hypo14} & 17 & 2 & 2 & - & 2 & 5 & 15 \\
\texttt{reduced} & 21 & 19 & 15 & 19 & - & 19 & 21 \\
\texttt{Union} & 21 & 14 & 5 & 16 & 2 & - & 20 \\
\texttt{trainer} & 11 & 0 & 1 & 6 & 0 & 1 & -
\end{tabular}
\label{tab:bot_vs_bot}
\caption{Wins of bots competing against each other}
\end{figure}

>>>>

\maketitle

@@

The game comes bundled with a number of bots with different styles, that are designed to pose a challenge to a wide range of human opponents. In order to define a clean ranking between them, we recorded the score of all possible lineups (figure \ref{tab:bot_vs_bot} contains the wins of bots in the row entry versus the column entry bot).

\begin{figure}[H]
\begin{tabular}{c|ccccccc}
vs. &
\texttt{Axji-0-2} &
\texttt{COM\_11} &
\texttt{GintonicV9} &
\texttt{Hypo14} &
\texttt{reduced} &
\texttt{Union} &
\texttt{trainer} \\
\hline
\texttt{Axji-0-2} & - & 0 & 0 & 4 & 0 & 0 & 10 \\
\texttt{COM\_11} & 21 & - & 9 & 19 & 6 & 16 & 20 \\
\texttt{GintonicV9} & 21 & 12 & - & 19 & 6 & 16 & 20 \\
\texttt{Hypo14} & 17 & 2 & 2 & - & 2 & 5 & 15 \\
\texttt{reduced} & 21 & 19 & 15 & 19 & - & 19 & 21 \\
\texttt{Union} & 21 & 14 & 5 & 16 & 2 & - & 20 \\
\texttt{trainer} & 11 & 0 & 1 & 6 & 0 & 1 & -
\end{tabular}
\label{tab:bot_vs_bot}
\caption{Scores of bots competing against each other}
\end{figure}
